A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.tex
Radically simplify analysis

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

We conducted a two-sample t-test to compare the average bill lengths
between male and female penguins. The null hypothesis (\(H_0\)) states
that there is no difference in bill lengths between male and female
penguins, while the alternative hypothesis (\(H_1\)) suggests a
significant difference.

The t-test was performed using the \texttt{t.test()} function in R, with
a significance level of 0.05.

@@

Descriptive statistics of the data set are displayed in Table 1.

\begin{table}
\caption{Summary Statistics}\tabularnewline

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]Q[]Q[]Q[]Q[]Q[]Q[]},
cell{1}{3}={c=2,}{halign=c,},
cell{1}{5}={c=2,}{halign=c,},
cell{1}{7}={c=2,}{halign=c,},
column{1}={halign=l,},
column{2}={halign=l,},
column{3}={halign=r,},
column{4}={halign=r,},
column{5}={halign=r,},
column{6}={halign=r,},
column{7}={halign=r,},
column{8}={halign=r,},
row{1}={halign=c,},
hline{8}={1,2,3,4,5,6,7,8}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
&  & Adelie (N=146) &  & Chinstrap (N=68) &  & Gentoo (N=119) &  \\ \cmidrule[lr]{3-4}\cmidrule[lr]{5-6}\cmidrule[lr]{7-8}
&    & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev. \\ \midrule %% TinyTableHeader
bill\_length\_mm    &           & \num{38.8}   & \num{2.7}   & \num{48.8}   & \num{3.3}   & \num{47.6}   & \num{3.1}   \\
bill\_depth\_mm     &           & \num{18.3}   & \num{1.2}   & \num{18.4}   & \num{1.1}   & \num{15.0}   & \num{1.0}   \\
flipper\_length\_mm &           & \num{190.1}  & \num{6.5}   & \num{195.8}  & \num{7.1}   & \num{217.2}  & \num{6.6}   \\
body\_mass\_g       &           & \num{3706.2} & \num{458.6} & \num{3733.1} & \num{384.3} & \num{5092.4} & \num{501.5} \\
year                  &           & \num{2008.1} & \num{0.8}   & \num{2008.0} & \num{0.9}   & \num{2008.1} & \num{0.8}   \\
&           & N             & Pct.         & N             & Pct.         & N             & Pct.         \\
island                & Biscoe    & \num{44}     & \num{30.1}  & \num{0}      & \num{0.0}   & \num{119}    & \num{100.0} \\
& Dream     & \num{55}     & \num{37.7}  & \num{68}     & \num{100.0} & \num{0}      & \num{0.0}   \\
& Torgersen & \num{47}     & \num{32.2}  & \num{0}      & \num{0.0}   & \num{0}      & \num{0.0}   \\
sex                   & female    & \num{73}     & \num{50.0}  & \num{34}     & \num{50.0}  & \num{58}     & \num{48.7}  \\
& male      & \num{73}     & \num{50.0}  & \num{34}     & \num{50.0}  & \num{61}     & \num{51.3}  \\
\bottomrule
\end{tblr}
\end{table}

The t-test revealed a significant difference in bill lengths between
male and female penguins (\(t(329.29) = -6.67, p < 0\.001\)). Female
penguins (\(M = 42.1\,\mathrm{mm}, SD = 4.9\,\mathrm{mm}\)) exhibited
shorter bill lengths compared to male penguins
(\(M = 45.85\,\mathrm{mm}, SD = 5.37\,\mathrm{mm}\)).

>>>>

\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

We conducted a Welch two-sample \emph{t}-test to compare the average
bill lengths between male and female penguins. The null hypothesis
(\(H_0\)) states that there is no difference in bill lengths between
male and female penguins, while the alternative hypothesis (\(H_1\))
suggests a significant difference.

The \emph{t}-test was performed using the \texttt{t.test()} function in
R, with a significance level of 0.05.

@@

Descriptive statistics of the data set are given in
Table~\ref{tbl-descriptive-statistics} and individual bill lengths are
displayed in Figure~\ref{fig-bill-length-comparison}.

The Welch Two Sample t-test testing the difference of bill\_length\_mm
by sex (mean in group female = 42.10, mean in group male = 45.85)
suggests that the effect is negative, statistically significant, and
large (difference = -3.76, 95\% CI {[}-4.87, -2.65{]}, t(329.29) =
-6.67, p \textless{} .001, Cohen's d = -0.73)

\begin{table}

{\caption{{Descriptive Statistics}{\label{tbl-descriptive-statistics}}}
\vspace{-20pt}}

\begin{longtable}[]{@{}lll@{}}
\toprule\noalign{}
Variable & female (n=165) & male (n=168) (n=333) \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
species {[}Adelie{]}, \% & 44.2 & 43.5 \\
species {[}Chinstrap{]}, \% & 20.6 & 20.2 \\
species {[}Gentoo{]}, \% & 35.2 & 36.3 \\
island {[}Biscoe{]}, \% & 48.5 & 49.4 \\
island {[}Dream{]}, \% & 37.0 & 36.9 \\
island {[}Torgersen{]}, \% & 14.5 & 13.7 \\
Mean bill\_length\_mm (SD) & 42.10 (4.90) & 45.85 (5.37) \\
Mean bill\_depth\_mm (SD) & 16.43 (1.80) & 17.89 (1.86) \\
Mean flipper\_length\_mm (SD) & 197.36 (12.50) & 204.51 (14.55) \\
Mean body\_mass\_g (SD) & 3862.27 (666.17) & 4545.68 (787.63) \\
year {[}2007{]}, \% & 30.9 & 31.0 \\
year {[}2008{]}, \% & 33.9 & 33.9 \\
year {[}2009{]}, \% & 35.2 & 35.1 \\
\end{longtable}

\end{table}
